Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.

Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out. It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded that there might be a small cultural effect in attitudes toward start-up activities.

Rather than trying to trace cultural patterns at large, we intend to focus on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person ????????????and his or her integration into social networks????????" [@OECD2009].

Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012 and the OECD PISA (Programme for International Student Assessment) LINK ????? also from 2012, there seem to be different amounts of entrepreneurial self-efficacy ?????and collectivism????? between countries. By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur. Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business.  Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle that would prevent the people surveyed from starting a business, despite the good opportunities they may perceive.

Variable | France | UK
-------------|---------------|---------
Fear of Failure (GEM 2012) | 43% | 36%
Perceived Capabilities (GEM 2012) | 36% | 47%
Sense of belonging (PISA 2012) | 47% | 79%

So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems. Specifically, we wonder to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many cultural and educational parameters differ but, one stands out that is the positive reinforcement effectively in use throughout the compulsory education system in the UK. We would like to verify if this has to do with the amount of self-efficacy mentioned above.

>>>>

More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities. Yet, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.

Rather than trying to trace cultural features at large, we intend to focus on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person" [@OECD2009].

Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012 and the OECD PISA (Programme for International Student Assessment) LINK ????? also from 2012, there seem to be different amounts of entrepreneurial self-efficacy between countries. By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur. Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business. Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.

Variable | France | UK
-------------|---------------|---------
Fear of Failure (GEM 2012) | 43% | 36%
Perceived Capabilities (GEM 2012) | 36% | 47%

So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems. Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, positive reinforcement is effectively in use throughout the compulsory education system in the UK. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
